---
title: "Gapminder Analysis"
author: "Evan Robinson"
date: "10/14/2019"
output:
  html_document:
    fig_caption: yes
    toc: yes
    keep_md: yes
---

# Introduction

Here is my first rmd document - this is where you'd be writing the text of your analysis or manuscript.

# Lets embed some r code

We'll write an R chunk that loads the tidyverse packaged and then reads in the Gapminder data set from the data subdirectory of the project.

Use ctrl+alt+i on a PC as quick key to insert new R chunk.

```{r, results='hide'}
library(tidyverse)
gm <- read_csv('Data/gapminder.csv')
```

# Investigate gm data

Let's take a look at the gm

```{r}
head(gm)
```

# Our first plot

showing gdp per capita on x and life expectancy on y

```{r, fig.cap = "Life Expectancy v. GDP"}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
```

Good practice to run all your code before you knit the code, so you can find any errors, otherwise it will fail (knit with ctrl+shift+k?)

# A better plot

```{r, fig.cap = "Life Expectancy v. GDP with color", fig.width=10, fig.height=10}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(col = continent)) +
  scale_x_log10()
```

# Possible chunk options

Options include:
- echo (TRUE by default) whether to include the code in the output
- results 
  - hide will hide the results (not usually helpful).
  - hold will hold results until the end of the R chunk (helpful if you want all of the code, and then all of the output).
- include (TRUE by default) if FALSE then code will be shown, but not run (say you had a view() in your code, and you just wanted to show someone that's what they should do, but not actually run within your document)
- fig.width, fig.height set the figure dimensions in your output
-cache (FALSE by default) if you want to reknit the document several times while you change colors etc, you can cahce the results of an R chunk - it will evaluate when you knit if that chunk has changed, and if it hasn't it will just pull up the saved result so it won't take a half-hour.

# Table in RMarkdown

See some data using head

```{r}
head(gm)
```

now we're going to turn that exat output as a nicely formatted table

```{r}
library(knitr)
kable(head(gm))

```

If you loke tables, look at **gt** table package - ** here makes bold, * makes italicized.

